---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# handbook

<!-- badges: start -->
<!-- badges: end -->

The goal of the package `handbook` is to provide data for some infrastructure to create graphics. 

## Installation

You can install the development version of handbook like so:

``` r
remotes::install_github("heike/handbook")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(handbook)
library(tidyverse)

## basic example code
```

### Color schemes

### Maps

The `statesmaps` object consists of polygons and hex shapes describing each state. Additionally, state names, abbreviations and fips codes are provided for linkage with data sources.

```{r maps}
head(statesmaps)
```
As an example to acquire data from the US Census Bureau we can use the code below, thanks to Kyle Walker's amazing [tidycensus](https://walker-data.com/tidycensus/articles/basic-usage.html) package:

```{r}
library(tidyverse)
library(tidycensus)
census_key <- "place your API key here"
census_key <- "7f784587c3918611ad6ca67188d9b269b3558dd4"
census_api_key(census_key)

# H012001 encodes the average houshold size
hh10 <- get_decennial(geography = "state",
                       variables = "H012001",
                       year = 2010)
map_values <- statesmaps %>% left_join(hh10, by = c("state_name" = "NAME"))
```

Once the data is joined with the mapping information, we can draw choropleth maps or hexbin maps:

```{r}
map_values %>% unnest(col=polygon) %>%
  ggplot(aes( x = long, y = lat, group = group, fill=value)) +
  geom_polygon(colour = "grey50", size=0.1) +
  #  geom_text (aes(label=id)) +
  theme_void () +
  coord_map () +
  scale_fill_gradient2("Avg. Houshold size", midpoint=median(hh10$value))
```

Note that only in the hexbin diagram we get to see the nation's territory with the smallest average household size: DC residents report in the 2010 census an average household size of 2.1 persons.

```{r}
map_values %>% unnest(col=hexagon) %>%
  ggplot(aes( x = long, y = lat, group = group, fill=value)) +
  geom_polygon(colour = "grey50", size=0.1) + 
  theme_void () +
  coord_map () +
  scale_fill_gradient2("Avg. Houshold size", midpoint=median(hh10$value))
```
